\documentclass[11pt,a4paper]{moderncv}

\usepackage{mathpazo}
\renewcommand{\sfdefault}{\rmdefault}

\usepackage[utf8]{inputenc}
\moderncvstyle{classic}                       
\moderncvcolor{blue}                        
\usepackage[scale=0.87]{geometry}
\setlength{\hintscolumnwidth}{2.5cm}         
\firstname{Aleksandr}
\familyname{Salatich}
\address{3/10 Kushelevskaya doroga street, 195220}{St. Petersburg, Russia}
\phone{+7(981)966-8126}
\quote{Ipse se nihil scire id unum sciat}
\title{Software Engineer}
\email{salatiques@gmail.com}
\extrainfo{LinkedIn: www.linkedin.com/in/571001124 \\ 
GitHub: www.github.com/Salatich}
\renewcommand\refname{Selected publications}
\nopagenumbers{} 

\begin{document}
\makecvtitle


\section{Personal details}
\cvline{Birth}{April 20, 1992}
\cvline{Marital status}{Married}
\cvline{Citizenship}{Russia}
\section{Education}
\cvline{2016-present}{\textbf{PhD Program, Information technology and numerical methods}
\newline \textit{Physics Faculty, Department of Computational Physics, St.Petersburg State University, Russia}}
\cvline{2014-2016}{\textbf{Master in Applied Mathematics and Physics}
\newline \textit{Physics Faculty, Department of Computational Physics, St.Petersburg State University, Russia}
\newline Master Thesis in June 2016 (grade 5 of 5): Development of Distolymp software subsystems (written in Russian) }
\cvline{2010-2014}{\textbf{Bachelor in Applied Mathematics and Physics}
\newline \textit{Physics Faculty, Department of Theoretical Physics, Omsk State University, Russia}
\newline Bachelor Thesis in July 2014 (grade 5 of 5): Simulation of dynamic phase transitions in Ising-like systems under a time-dependent oscillating external field   (written in Russian) }

\section{Work experience and projects}
\cvline{2018-present}{\textbf{Middle Software Engineer}
\newline \textit{EPAM Systems}
\newline \url{epam.com}
\newline Development ETL jobs via Scala Spark/Hive inside on-premise Hadoop cluster
}

\cvline{2017-2018}{\textbf{Junior/Middle Java Developer}
\newline \textit{Rostelecom Contact-Center}
\newline \url{omnichat.ru}
\newline Development software for communication with customers through digital channels. Add new functionality, bug fixing and refactoring of existing microservice architecture software using Design Patterns (Visitor, Factory, Command etc.). Add new API methods (Spring, Hibernate, PostgreSQL, OracleDB) for receiving messages from customers through messengers, social networks and site : telegram, viber, vk, facebook, widget. Development of new microservices (Spring, ActiveMQ, RabbitMQ). Test coverage of code via unit and integration tests (JUnit, Mockito). Code review (Bitbucket, GitLab). Installing updates  with DevOps team (Jenkins, Docker, Tomcat, Glassfish, WebLogic). Communication with Delivery Managers to formation of requirements. Communication with Scrum Master to task evaluation and distribution of tasks among small developers team
}

\cvline{2017}{\textbf{Junior Full Stack Developer}
\newline \textit{JSC Bank <<PSCB>>}
\newline \url{online.pscb.ru}
\newline Development Payment Aggregator and Payment System (e-commerce). Add new functionality to existing payment system. Add new API methods for payments processing (Grails Framework)  on server side. Add new buttons, events and templates (JavaScript, Ajax, JSP templating) on client side 
}

\cvline{2014-2016}{\textbf{Junior PHP Developer}
\newline \textit{St.Petersburg State University}
\newline \url{distolymp2.spbu.ru}
\newline Development of Distolymp program complex for conduction Online Competition in Physics (part-time employment). Add new functions and submodules (PHP, JavaScript, Ajax) to current system
}

\section{Skills}
\cvline{}{\textbf{Programming languages:} Java, Groovy, Python, SQL}
\cvline{}{\textbf{Frameworks:} Spring Framework, Hibernate, JUnit, Mockito, Hadoop, Spark, Apache Hive, Apache Maven, Grails}
\cvline{}{\textbf{Industry Knowledge:} Agile, SOLID}
\cvline{}{\textbf{Databases:} PostgreSQL, Oracle}
\cvline{}{\textbf{Tools \& Technologies:} Apache Kafka, Jackson, RabbitMQ, ActiveMQ, Jira}
\cvline{}{\textbf{Java application servers:} Tomcat, GlassFish, WebLogic}
\cvline{}{\textbf{IDEs:} IntelliJ IDEA, NetBeans}
\cvline{}{\textbf{VCS:} Git, SVN}
\cvline{}{\textbf{Continuous Integration:} Jenkins}
\cvline{}{\textbf{Virtualization:} Docker, Oracle VM VirtualBox}
\cvline{}{\textbf{Mathematical software:} Maple, SymPy}
\cvline{}{\textbf{Document preparation systems:} \LaTeX, Microsoft Office}
\cvline{}{\textbf{OS:} Linux, Microsoft Windows}

\section{Additional Information}
\subsection{Conferences and publications}
\cvline{2018}{\textbf{Confluent Heun equation and equivalent first-order systems}
\newline Polynomial Computer Algebra 2018
\newline \url{https://pca-pdmi.ru/2018/files/21/pca18n.pdf}
}
\cvline{2017}{\textbf{Confluent Heun equation and confluent hypergeometric equation}
\newline Zap. Nauchn. Sem. POMI
\newline \url{https://link.springer.com/article/10.1007/s10958-018-3865-2}
}
\cvline{2015}{\textbf{A Distribution Model for Fuels Production and Consumption in the World}
\newline International Student Conference, Science and Progress, St.Petersburg, Peterhof}
\cvline{2015}{\textbf{Distolymp multi-platform program complex for testing knowledge and practical skills}
\newline \textit{Modern Information Technology. Theory and practice}
\newline Proceedings of the 2nd All-Russian Research-to-Practice Conference, Cherepovets}
\subsection{Additional Education}
\cvline{2013}{\textbf{Advanced Training Course}
\newline\textit{Institute of Mathematics and Information Technologies, Omsk State University, Russia}
\newline Introduction to Programming}
\cvline{}{\textbf{Stepic} \newline Java. Basic Course
\newline Algorithms: theory and practice. Methods
\newline Introduction to Computer Architecture. Elements of Operating Systems}
\cvline{}{\textbf{Coursera} \newline Machine Learning (Stanford)}
\end{document} 